Results

### 2024-03-20 Analysis/brms_learning.qmd
bunch of re-renders, and some new writing

---
title: "Bayesian Mixed Effects Models - Training Data"
subtitle: "Fitting mixed effects models"
date: last-modified
categories: [Analysis, R, Bayesian]
code-fold: true
---

>>>>

---
title: "Bayesian Mixed Effects Models - Training Data"
subtitle: "Fitting mixed effects models"
date: last-modified
categories: [Analysis, R, Bayesian]
code-fold: true
execute: 
  enabled: false
  eval: false
---

### 2024-03-20 Analysis/combo_test.qmd
bunch of re-renders, and some new writing

ep1 <- d |>
  filter(expMode2 == "Test") |>
  group_by(condit, bandType, fb, bandOrder, vb) |>  # No need for 'id' if not used later
  summarise(se_dist = sd(dist) / sqrt(n()),dist = mean(dist)) |>
  ggplot(aes(x = condit, y = dist, fill = vb, pattern=bandType)) +
   geom_bar_pattern(stat = "identity", 
                    position = position_dodge()) + 
  geom_errorbar(aes(ymin = dist - se_dist, ymax = dist + se_dist),position = position_dodge()) +
  facet_wrap2(~fb*bandOrder,axes="all") +
  labs(title="Testing Deviation",pattern = "Band Type") +
   scale_pattern_manual(values = c("stripe", "circle"))

ep2 <- d |>
  filter(expMode2 == "Test") |>
  group_by(condit, bandType, fb, bandOrder, vb) |>  # No need for 'id' if not used later
  summarise(se_dist = sd(dist) / sqrt(n()),dist = mean(dist)) |>
  ggplot(aes(x = vb, y = dist, fill = condit, pattern=bandType)) +
   geom_bar_pattern(stat = "identity", 
                    position = position_dodge()) + 
  geom_errorbar(aes(ymin = dist - se_dist, ymax = dist + se_dist),position = position_dodge()) +
  facet_wrap2(~fb*bandOrder,axes="all") +
  labs(title="Testing Deviation",pattern = "Band Type") +
   scale_pattern_manual(values = c("stripe", "circle"))

>>>>

ep1 <- d |>
  filter(expMode2 == "Test") |>
  group_by(condit, bandType, fb, bandOrder, vb) |>  # No need for 'id' if not used later
  summarise(se_dist = sd(dist) / sqrt(n()),dist = mean(dist)) |>
  ggplot(aes(x = condit, y = dist, fill = vb,
             pattern=bandType,
             pattern_density=0.35,
             pattern_fill=bandType, 
             ppatern_angle=bandType,
            )) +
   geom_bar_pattern(stat = "identity", 
                   # pattern_density=.25,
                    position = position_dodge()) + 
  geom_errorbar(aes(ymin = dist - se_dist, ymax = dist + se_dist),position = position_dodge()) +
  facet_wrap2(~fb*bandOrder,axes="all") +
  labs(title="Testing Deviation",pattern = "Band Type") +
  # scale_pattern_manual(values = c("stripe", "circle"))
  scale_pattern_spacing_discrete(range = c(0.01, 0.05))

ep2 <- d |>
  filter(expMode2 == "Test") |>
  group_by(condit, bandType, fb, bandOrder, vb) |>  # No need for 'id' if not used later
  summarise(se_dist = sd(dist) / sqrt(n()),dist = mean(dist)) |>
  ggplot(aes(x = vb, y = dist, fill = condit, pattern=bandType)) +
   geom_bar_pattern(stat = "identity",

                    position = position_dodge()) + 
  geom_errorbar(aes(ymin = dist - se_dist, ymax = dist + se_dist),position = position_dodge()) +
  facet_wrap2(~fb*bandOrder,axes="all") +
  labs(title="Testing Deviation",pattern = "Band Type") +
   scale_pattern_manual(values = c("stripe", "circle"))

### 2024-03-20 Analysis/e1.qmd
bunch of re-renders, and some new writing

---
title: "HTW E1"
author:
  - name: Thomas Gorman
    corresponding: true
categories: [Analyses, R, Bayesian]
toc: false
format-links: false
page-layout: full
cache: true
code-fold: true
cold-tools: true
lightbox: true
# execute: 
#   cache: true
#keep-md: true
format:
  html: default
  # hikmah-manuscript-pdf:
  #   echo: false
  #   output-file: "hikmah-e1.pdf"
  #   mainfont: "Linux Libertine O"
  #   mainfontoptions:
  #     - "Numbers=Proportional"
  #     - "Numbers=OldStyle"
  #   mathfont: "Libertinus Math"
  # hikmah-pdf:
  #   echo: false
  #   cite-method: citeproc
  #   output-file: "hikmah.pdf"
  #   mainfont: "Linux Libertine O"
  #   mainfontoptions:
  #     - "Numbers=Proportional"
  #     - "Numbers=OldStyle"
  #   sansfont: "IBM Plex Sans"
  #   mathfont: "Libertinus Math"
  #   geometry:
  #     - top=1in     
  #     - bottom=1in  
  #     - left=1in    
  #     - right=1in  
  #     - heightrounded
  #   # linestretch: 1.05
  #   include-in-header:
  #     # The \everydisplay thing makes all math blocks use \small font
  #     text: |
  #       \usepackage{mathtools}
  #       \everydisplay\expandafter{\the\everydisplay\small}
  #       \usepackage{float}
  #       \floatplacement{figure}{H}
  #       \floatplacement{table}{H}
  # pdf: 
  #   echo: false
  #   documentclass: article
  #   papersize: a4
  #   geometry:
  #     - left=2cm
  #     - right=2cm
  #     - top=2cm
  #     - bottom=2cm
  # ipynb: default
  hugo-md:
    echo: false
    html-math-method: mathjax
    output-file: e1-hugo.md
  gfm:
    echo: true
    output-file: e1-gfm.md
  # docusaurus-md:
  #   echo: true
  #   output-file: e1-docusaurus.md
#prefer-html: false
---

@@

```{r}
#| label: fig-e1-train-dev
#| fig-cap: E1. Deviations from target band across training blocks. 
#| eval: FALSE
p1 <- trainE1 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
    stat_summary(geom = "line", fun = mean) +
    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
    facet_wrap(~vb)+
    scale_x_continuous(breaks = seq(1, nbins + 1)) +
    theme(legend.title=element_blank()) + 
    labs(y = "Deviation", x="Training Block") 
#ggsave(here("Assets/figs/e1_train_deviation.png"), p1, width = 8, height = 4,bg="white")

::: {#fig-e1-train-dev}

![](../Assets/figs/e1_train_deviation.png)

E1. Deviations from target band during training
:::

@@

```{r}
#| label: fig-e1-test-dev
#| fig-cap: E1. Deviations from target band during testing without feedback stage. 
#| eval: FALSE
pe1td <- testE1 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
  labs(x="Band", y="Deviation From Target")

@@

p2 <- (pe1td + pe1ce) + plot_annotation(tag_levels= 'A')
#ggsave(here::here("Assets/figs", "e1_test-dev.png"), p2, width=8, height=4, bg="white")

@@

Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant. See @tbl-e1-bmm-vx for the full model results. The estimated coefficient for training condition ($\beta$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\]) suggests that the varied group tends to produce harder throws than the constant group, but is not in and of itself useful for assessing discrimination. Most relevant to the issue of discrimination is the slope on Velocity Band ($\beta$ = `r sc1$estimate` 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]). Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands. The estimate for the interaction between slope and condition ($\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]), suggests that the discrimination was somewhat modulated by training condition, with the varied participants showing less sensitivity between bands than the constant condition. This difference is depicted visually in @fig-e1-test-vx.

```{r}
#| label: fig-e1-test-vx
#| fig-cap: Experiment 1. Conditional effect of training condition and Band. Ribbons indicate 95% HDI. The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands. 
#| fig-height: 16
#| fig-width: 12
#| eval: FALSE

pe1tv <- testE1 %>% group_by(id,vb,condit) |> plot_distByCondit()

@@

p3 <- pe1tv / (pe1vce + pid_den1 + pid_slopes1) + plot_annotation(tag_levels= 'A')
#ggsave(here::here("Assets/figs", "e1_test-vx.png"), p3,width=9,height=11, bg="white",dpi=600)
p3
```

{{< pagebreak >}}

::: {#fig-e1-test-vx}

![](../Assets/figs/e1_test-vx.png)

Experiment 1. Conditional effect of training condition and Band. Ribbons indicate 95% HDI. The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.

{{< pagebreak >}}

@@

## References

::: {#refs}
:::

>>>>

---
title: "Experiment 1"
categories: [Analyses, R, Bayesian]
toc: false
format-links: false
page-layout: full
code-fold: true
cold-tools: true
lightbox: true
execute:
  #cache: true
  warning: false
format:
  html: default
  # hugo-md:
  #   echo: false
  #   html-math-method: mathjax
  #   output-file: e1-hugo.md
  # gfm:
  #   echo: true
  #   output-file: e1-gfm.md
  # docusaurus-md:
  #   echo: true
  #   output-file: e1-docusaurus.md
#prefer-html: false
---

@@

```{r}
#| label: fig-e1-train-dev
#| fig-cap: E1. Deviations from target band across training blocks. 
#| eval: true
p1 <- trainE1 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
    stat_summary(geom = "line", fun = mean) +
    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
    facet_wrap(~vb)+
    scale_x_continuous(breaks = seq(1, nbins + 1)) +
    theme(legend.title=element_blank()) + 
    labs(y = "Deviation", x="Training Block") 
#ggsave(here("Assets/figs/e1_train_deviation.png"), p1, width = 8, height = 4,bg="white")
p1
```

@@

```{r}
#| label: fig-e1-test-dev
#| fig-cap: E1. Deviations from target band during testing without feedback stage. 
#| eval: TRUE
pe1td <- testE1 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
  labs(x="Band", y="Deviation From Target")

@@

p2 <- (pe1td + pe1ce) + plot_annotation(tag_levels= 'A')
#ggsave(here::here("Assets/figs", "e1_test-dev.png"), p2, width=8, height=4, bg="white")
p2

@@

Finally, to assess the ability of both conditions to discriminate between velocity bands, we fit a model predicting velocity as a function of training condition and velocity band, with random intercepts and random slopes for each participant. See @tbl-e1-bmm-vx for the full model results. The estimated coefficient for training condition ($\beta$ = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\]) suggests that the varied group tends to produce harder throws than the constant group, but is not in and of itself useful for assessing discrimination. Most relevant to the issue of discrimination is the coefficient on the Band predictor ($\beta$ = `r sc1$estimate` 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]). Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands. The estimate for the interaction between slope and condition ($\beta$ = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\]), suggests that the discrimination was somewhat modulated by training condition, with the varied participants showing less sensitivity between bands than the constant condition. This difference is depicted visually in @fig-e1-test-vx.

```{r}
#| label: fig-e1-test-vx
#| fig-cap: E1 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
#| fig-width: 11
#| fig-height: 9

testE1 %>% group_by(id,vb,condit) |> plot_distByCondit()

```{r}
#| label: tbl-e1-bmm-vx
#| fig-cap: Experiment 1. Conditional effect of training condition and Band. Ribbons indicate 95% HDI. The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands. 
#| fig-height: 12
#| fig-width: 11
#| eval: TRUE

@@

p3 <- (pe1vce + pid_den1 + pid_slopes1) + plot_annotation(tag_levels= 'A')
#ggsave(here::here("Assets/figs", "e1_test-vx.png"), p3,width=9,height=11, bg="white",dpi=600)
p3
```

@@

### 2024-03-20 Analysis/e2.qmd
bunch of re-renders, and some new writing

---
title: "Experiment 2"
categories: [Analyses, R, Bayesian]
toc: false
format-links: false
page-layout: full
#cache: true
code-fold: true
cold-tools: true
lightbox: true
execute:
  cache: true
  warning: false
# keep-md: true
format:
  html: default
  hugo-md:
    echo: false
    html-math-method: mathjax
    output-file: e2-hugo.md
  # gfm:
  #   echo: true
  #   output-file: e2-gfm.md
---

@@

```{r}
#| label: fig-e2-train-dev
#| fig-cap: E2. Deviations from target band across training blocks. 
#| eval: FALSE
p1 <- trainE2 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
    stat_summary(geom = "line", fun = mean) +
    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
    facet_wrap(~vb)+
    scale_x_continuous(breaks = seq(1, nbins + 1)) +
    theme(legend.title=element_blank()) + 
    labs(y = "Deviation", x="Training Block") 
#ggsave(here("Assets/figs/e2_train_deviation.png"), p1, width = 8, height = 4,bg="white")

::: {#fig-e2-train-dev}

![](../Assets/figs/e2_train_deviation.png)

E2. Deviations from target band across training blocks. 
:::

@@

```{r}
#| label: fig-e2-test-dev
#| fig-cap: E2. Deviations from target band during testing without feedback stage. 
#| eval: FALSE
pe2td <- testE2 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
  labs(x="Band", y="Deviation From Target")

@@

p2 <- (pe2td + pe2ce) + plot_annotation(tag_levels= 'A')
#ggsave(here::here("Assets/figs", "e2_test-dev.png"), p2, width=8, height=4, bg="white")
```

::: {#fig-e2-test-dev}

![](../Assets/figs/e2_test-dev.png)

E2. A) Deviations from target band during testing without feedback stage. B) Estimated marginal means for the interaction between training condition and band type. Error bars represent 95% confidence intervals.
:::

@@

```{r}
#| label: e2_test-vx
#| fig-cap: Conditional effect of training condition and Band. Ribbons indicate 95% HDI. The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands. 
#| fig-height: 16
#| fig-width: 12
#| eval: FALSE

pe2tv <- testE2 %>% group_by(id,vb,condit) |> plot_distByCondit()

@@

p3 <- pe2tv / (pe2vce + pid_den2 + pid_slopes2) + plot_annotation(tag_levels= 'A')
#ggsave(here::here("Assets/figs", "e2_test-vx.png"), p3,width=9,height=11, bg="white",dpi=600)
#p3
```

{{< pagebreak >}}

::: {#fig-e2-test-vx}

![](../Assets/figs/e2_test-vx.png)

Experiment 2. Conditional effect of training condition and Band. Ribbons indicate 95% HDI. The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.

>>>>

---
title: "Experiment 2"
categories: [Analyses, R, Bayesian]
toc: false
format-links: false
page-layout: full
#cache: true
code-fold: true
cold-tools: true
lightbox: true
execute:
  #cache: true
  warning: false
# keep-md: true
format:
  html: default
  # hugo-md:
  #   echo: false
  #   html-math-method: mathjax
  #   output-file: e2-hugo.md
  # gfm:
  #   echo: true
  #   output-file: e2-gfm.md
---

@@

```{r}
#| label: fig-e2-train-dev
#| fig-cap: E2. Deviations from target band across training blocks. 
#| eval: TRUE
p1 <- trainE2 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
    stat_summary(geom = "line", fun = mean) +
    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
    facet_wrap(~vb)+
    scale_x_continuous(breaks = seq(1, nbins + 1)) +
    theme(legend.title=element_blank()) + 
    labs(y = "Deviation", x="Training Block") 
#ggsave(here("Assets/figs/e2_train_deviation.png"), p1, width = 8, height = 4,bg="white")
p1
```

@@

```{r}
#| label: fig-e2-test-dev
#| fig-cap:  A) Deviations from target band during testing without feedback stage. B) Estimated marginal means for the interaction between training condition and band type. Error bars represent 95% confidence intervals.
#| eval: TRUE

condEffects <- function(m,xvar){
  m |> ggplot(aes(x = {{xvar}}, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() + 
  stat_halfeye(alpha=.1, height=.5) +
  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

}
pe2td <- testE2 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
  theme(legend.title=element_blank(),axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +
  labs(x="Band", y="Deviation From Target")

@@

p2 <- (pe2td + pe2ce) + plot_annotation(tag_levels= 'A')
#ggsave(here::here("Assets/figs", "e2_test-dev.png"), p2, width=8, height=4, bg="white")
p2
```

@@

```{r}
#| label: fig-e2-test-vx
#| fig-cap: E2 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
#| fig-width: 11
#| fig-height: 9
testE2 %>% group_by(id,vb,condit) |> plot_distByCondit()

```{r}
#| label: tbl-e2-bmm-vx
#| fig-cap: Conditional effect of training condition and Band. Ribbons indicate 95% HDI. The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands. 
#| fig-height: 12
#| fig-width: 11
#| eval: TRUE

@@

p3 <- (pe2vce + pid_den2 + pid_slopes2) + plot_annotation(tag_levels= 'A')
#ggsave(here::here("Assets/figs", "e2_test-vx.png"), p3,width=9,height=11, bg="white",dpi=600)
p3
```

### 2024-03-20 Analysis/e3.qmd
bunch of re-renders, and some new writing

---
title: "Experiment 3"
categories: [Analyses, R, Bayesian]
toc: false
format-links: false
page-layout: full
lightbox: true
code-fold: true
cold-tools: true
execute:
  cache: true
  warning: false
#keep-md: true
format:
  html: default
  hugo-md:
    echo: false
    html-math-method: mathjax
    output-file: e3-hugo.md
  # gfm:
  #   echo: true
  #   output-file: e3-gfm.md
---

@@

```{r}
#| label: fig-e3-train-dev
#| fig-cap: E3. Deviations from target band during testing without feedback stage. 
#| eval: FALSE
p1 <- trainE3 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
    stat_summary(geom = "line", fun = mean) +
    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
    ggh4x::facet_nested_wrap(~bandOrder*vb,ncol=3)+
    scale_x_continuous(breaks = seq(1, nbins + 1)) +
    theme(legend.title=element_blank()) + 
    labs(y = "Deviation", x="Training Block") 
#ggsave(here("Assets/figs/e3_train_deviation.png"), p1, width = 9, height = 8,bg="white")
```

::: {#fig-e3-train-dev}

![](../Assets/figs/e3_train_deviation.png)

E3. Deviations from target band across training blocks. 
:::

@@

```{r}
#| label: fig-e3-test-dev
#| fig-cap: E3. Deviations from target band during testing without feedback stage. 
#| eval: FALSE

@@

}
pe3ce <- bmtd3 |> emmeans( ~condit *bandOrder*bandType) |>
  gather_emmeans_draws() |>
 condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type") + 
 facet_wrap(~bandOrder,ncol=1)

p2 <- pe3td + pe3ce + plot_annotation(tag_levels= 'A')
#ggsave(here::here("Assets/figs", "e3_test-dev.png"), p2, width=9, height=8, bg="white")

::: {#fig-e3-test-dev}

![](../Assets/figs/e3_test-dev.png)

E3. A) Deviations from target band during testing without feedback stage. B) Estimated marginal means for the interaction between training condition and band type. Error bars represent 95% confidence intervals.
:::

### Discimination

```{r}
#| label: tbl-e3-bmm-vx
#| tbl-cap: "Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"

@@

```{r}
#| label: fig-e3-bmm-vx
#| fig-cap: Conditional effect of training condition and Band. Ribbons indicate 95% HDI. The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands. 
#| fig-height: 9
#| fig-width: 12
#| eval: FALSE
pe3tv <- testE3 %>% group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")

@@

p3 <- pe3tv / (pe3vce + pid_den3 + pid_slopes3) + plot_annotation(tag_levels= 'A')
#ggsave(here::here("Assets/figs", "e3_test-vx.png"), p3,width=11,height=13, bg="white",dpi=800)
#p3

  # vbRect<- testE3 |> group_by(vb) |>
  #   summarise(lowBound=first(bandInt),highBound=first(highBound)) |> 
  #   mutate(vbn=as.numeric(vb), rectWidth=.2,
  #          vbLag=vbn-rectWidth,vbLead=vbn+rectWidth)

  # bandLines4 <- list(geom_segment(data=vbRect,aes(x=vbLag,xend=vbLead,y=highBound,yend=highBound),alpha=1,linetype="dashed"),
  #                  geom_segment(data=vbRect,aes(x=vbLag,xend=vbLead,y=lowBound,yend=lowBound),alpha=1,linetype="dashed"),
  #                  geom_text(data=vbRect,aes(x=vbLag-.03,y=lowBound+100,label=vb),angle=90,size=3.5,fontface="bold") )

# testE3 |>
#    select(id,condit,bandOrder,vb,band,lowBound,highBound,vx) |>
#   group_by(id,condit,bandOrder,vb,highBound) |> 
#   summarize(vx=mean(vx)) |> 
#   group_by(condit,bandOrder,vb,highBound) |>
#   summarise(mvx=mean(vx),sdvx=sd(vx), n=n(),se= sdvx/sqrt(n),.groups="drop" ) |>
#   mutate(vbn=highBound-200, rectWidth=.2,
#           band_index=as.numeric(factor(vb)),
#           rectX = as.numeric(condit) ) |>
#   ggplot(aes(x=condit,y=mvx,group=vb)) +
#   geom_bar(stat="identity",aes(fill=vb),position="dodge") +
#   geom_errorbar(aes(ymin=mvx-se,ymax=mvx+se,group=vb),position="dodge",width=.9,alpha=.5) +
#   geom_segment(aes(x=band_index-.25,xend=rectX+.05,y=highBound,yend=highBound, col=vb,group=vb),
#                alpha=.8,linetype="dashed",position = "dodge") +
#   # geom_hline(data=vbRect,aes(yintercept=vbn,col=vb),alpha=.5,linetype="dashed") +
#   # geom_hline(data=vbRect,aes(yintercept=highBound,col=vb),alpha=.5,linetype="dashed") +
#   scale_x_discrete(labels = c("Constant", "Varied")) +
#   scale_y_continuous(expand=expansion(add=100),breaks=round(seq(0,2000,by=200),2)) +
#   facet_wrap(~bandOrder,ncol=1)
  # geom_rect(aes(xmin = rectX-.3, xmax = rectX+.3,
  #               ymin = vbn, ymax = highBound),
  #           col="black",linetype="dashed",
  #         position = position_dodge(width = 1),
  #           alpha = 0.1)  +

@@

```{r}
#| eval: false
#| include: false

fe <- fixef(e3_vxBMM)[,1]
fixed_effect_Intercept <- fe["Intercept"]
fixed_effect_bandInt <- fe["bandInt"]
fixed_effect_interaction1 <- fe["conditVaried:bandInt"]
fixed_effect_interaction2 <- fe["bandOrderReverse:bandInt"]
fixed_effect_interaction3 <- fe["conditVaried:bandOrderReverse:bandInt"]

re <- data.frame(ranef(e3_vxBMM, pars = "bandInt")$id[, ,'bandInt']) %>% 
  rownames_to_column("id") %>% 
  left_join(e3Sbjs, by = "id") %>%
  mutate(intercept = fixed_effect_Intercept + fe["conditVaried"]*(condit=="Varied") + 
           fe["bandOrderReverse"]*(bandOrder=="Reverse") +
           fe["conditVaried:bandOrderReverse"]*(condit=="Varied" & bandOrder=="Reverse"), 
         adjust = fixed_effect_bandInt + fixed_effect_interaction1 * (condit == "Varied") + 
         fixed_effect_interaction2 * (bandOrder == "Reverse") + 
         fixed_effect_interaction3 * (condit == "Varied" & bandOrder == "Reverse"),
         slope = Estimate + adjust)

slopes <- re |>
  group_by(condit, bandOrder) |>
  summarize(
    intercept = mean(intercept),
    slope = mean(slope)
  )

plot_data <- e3 |> distinct(condit, bandOrder, bandInt) |> 
  left_join(slopes, by = c("condit", "bandOrder")) |>
  mutate(pred_y=intercept + slope*bandInt) |> arrange(condit,bandOrder,bandInt)

#a_line <- function(x,intercept,slope) (slope * x) +int

plot_data |> 
  ggplot(aes(x=bandInt,y=pred_y,color=interaction(condit, bandOrder))) +
  geom_point() +
  geom_abline(
    mapping = aes(
      intercept = intercept,
      slope = slope, 
      color = interaction(condit, bandOrder)
    ),size = 1.2) + 
  coord_equal() + theme(legend.title=element_blank())

{{< pagebreak >}}

::: {#fig-e3-test-vx}

![](../Assets/figs/e3_test-vx.png)

Experiment 3. Conditional effect of training condition and Band. Ribbons indicate 95% HDI. The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands.

>>>>

---
title: "Experiment 3"
categories: [Analyses, R, Bayesian]
toc: false
format-links: false
page-layout: full
lightbox: true
code-fold: true
cold-tools: true
execute:
  #cache: true
  warning: false
#keep-md: true
format: 
  html:
    column: 
      - screen-inset-right
  # hugo-md:
  #   echo: false
  #   html-math-method: mathjax
  #   output-file: e3-hugo.md
  # gfm:
  #   echo: true
  #   output-file: e3-gfm.md
---

@@

```{r}
#| label: fig-e3-train-dev
#| fig-cap: E3. Deviations from target band during testing without feedback stage. 
#| eval: true
p1 <- trainE3 |> ggplot(aes(x = Trial_Bin, y = dist, color = condit)) +
    stat_summary(geom = "line", fun = mean) +
    stat_summary(geom = "errorbar", fun.data = mean_se, width = .4, alpha = .7) +
    ggh4x::facet_nested_wrap(~bandOrder*vb,ncol=3)+
    scale_x_continuous(breaks = seq(1, nbins + 1)) +
    theme(legend.title=element_blank()) + 
    labs(y = "Deviation", x="Training Block") 
#ggsave(here("Assets/figs/e3_train_deviation.png"), p1, width = 9, height = 8,bg="white")
p1
```

@@

```{r}
#| label: fig-e3-test-dev
#| fig-cap: E3. A) Deviations from target band during testing without feedback stage. B) Estimated marginal means for the interaction between training condition and band type. Error bars represent 95% confidence intervals.
#| eval: true

}

@@

pe3ce <- bmtd3 |> emmeans( ~condit *bandOrder*bandType) |>
  gather_emmeans_draws() |>
 condEffects(bandType) + labs(y="Absolute Deviation From Band", x="Band Type") + 
 facet_wrap(~bandOrder,ncol=1)

p2 <- pe3td + pe3ce + plot_annotation(tag_levels= 'A')
#ggsave(here::here("Assets/figs", "e3_test-dev.png"), p2, width=9, height=8, bg="white")
p2
```

```{r}
##| label: tbl-e3-bmm-vx
##| tbl-cap: "Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"

@@

```{r}
#| label: fig-e3-test-vx
#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
#| fig-width: 11
#| fig-height: 10
##| column: screen-inset-right
# testE3 |> filter(bandOrder=="Original")|> group_by(id,vb,condit) |> plot_distByCondit()
# testE3 |> filter(bandOrder=="Reverse")|> group_by(id,vb,condit) |> plot_distByCondit() +ggtitle("test")

testE3 |> group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + 
   ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")
```

```{r}
#| label: fig-e3-bmm-vx
#| fig-cap: Conditional effect of training condition and Band. Ribbons indicate 95% HDI. The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands. 
#| fig-height: 10
#| fig-width: 11
##| eval: FALSE
# pe3tv <- testE3 %>% group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + ggh4x::facet_nested_wrap(bandOrder~condit,scale="free_x")

}

@@

p3 <- (pe3vce + pid_den3 + pid_slopes3) + plot_annotation(tag_levels= 'A')

#ggsave(here::here("Assets/figs", "e3_test-vx.png"), p3,width=11,height=13, bg="white",dpi=800)
p3

@@

### 2024-03-20 Sections/Intro.qmd
bunch of re-renders, and some new writing

>>>>

## Overview Of Present Study

The present study investigates the influence of training variability on learning, generalization, and extrapolation in a uni-dimensional visuomotor function learning task. To the best of our knowledge, this research is the first to employ the classic constant vs. varied training manipulation, commonly used in the literature on the benefits of variability, in the context of a uni-dimensional function learning task. Across three experiments,  we compare constant and varied training  conditions in terms of learning performance, extrapolation accuracy, and the ability to reliably discriminate between stimuli.

To account for the empirical results, we will apply a series of computational models, including the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM). Notably, this study is the first to employ approximate Bayesian computation (ABC) to fit these models to individual subject data, enabling us to thoroughly investigate the full range of posterior predictions of each model, and to  examine the the ability of these influential models of function learning to account for both the group level and individual level data.

### 2024-03-20 Sections/Results.qmd
bunch of re-renders, and some new writing

---
title: "Results"
author: "Thomas Gorman"
toc: true
toc-depth: 5
toc-expand: true
number-sections: true
number-depth: 5
strip-comments: true
echo: false
#toc: true
# toc-title: Contents
# toc-depth: 4
# toc-expand: 1
# execute:
#   echo: false
---

@@

{{< include ../Analysis/E1_test.qmd >}}

@@

{{< include ../Analysis/E2_test.qmd >}}

@@

{{< include ../Analysis/E3_test.qmd >}}

>>>>

---
title: Results
author: "Thomas Gorman"
toc: true
toc-depth: 5
toc-expand: true
number-sections: true
number-depth: 5
strip-comments: true
cold-tools: true
echo: false
format: 
  html:
    column: 
      - screen-inset-right
  hugo-md:
    echo: false
    html-math-method: mathjax
    output-file: full-results-hugo.md
  # gfm:
  #   echo: true
  #   output-file: e1-gfm.md
#toc: true
# toc-title: Contents
# toc-depth: 4
# toc-expand: 1
# execute:
#   echo: false
---

@@

{{< include ../Analysis/e1.qmd >}}

@@

{{< include ../Analysis/e2.qmd >}}

@@

{{< include ../Analysis/e3.qmd >}}

## Results Summary

## Overall Summary of Experiments 1-3

Across three experiments, we investigated the impact of training variability on learning, transfer, and extrapolation in a visuomotor function learning task. In Experiment 1, participants in the varied training condition, who experienced a wider range of velocity bands during training, showed lower accuracy at the end of training compared to those in the constant training condition. Crucially, during the testing phase, the varied group exhibited significantly larger deviations from the target velocity bands, particularly for the extrapolation bands that were not encountered during training. The varied group also showed less discrimination between velocity bands, as evidenced by shallower slopes when predicting response velocity from target velocity band.

Experiment 2 extended these findings by reversing the order of the training and testing bands. Similar to Experiment 1, the varied group demonstrated poorer performance during both training and testing phases. However, unlike Experiment 1, the varied group did not show a significant difference in discrimination between bands compared to the constant group.

In Experiment 3, we introduced an ordinal feedback system during training, in contrast to the continuous feedback provided in the previous experiments. Participants were assigned to both an order condition (original or reverse) and a training condition (constant or varied). The varied condition showed larger deviations at the end of training, consistent with the previous experiments. Interestingly, there was a significant interaction between training condition and band order, with the varied condition showing greater accuracy in the reverse order condition. During testing, the varied group once again exhibited larger deviations, particularly for the extrapolation bands. The reverse order conditions showed smaller deviations compared to the original order conditions. Discrimination between velocity bands was poorer for the varied group in the original order condition, but not in the reverse order condition.

In summary, these experiments consistently demonstrated that training with greater variability led to lower accuracy during both training and testing phases, with the detrimental effect being more pronounced for extrapolation items. The varied training condition also tended to show less discrimination between velocity bands, although this effect was modulated by the order of the training and testing bands. These findings suggest that while variable training can hinder initial learning, it may have differential effects on transfer and extrapolation depending on the specific task structure and the range of stimuli encountered during training and testing.

## References

::: {#refs}
:::
